Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-25 analysis/paper/paper.Rmd
Add new figure of overall scores and revise aggregated scores to include NA
This addressed Reviewer 1's comments about not showing all data.

The scores for all values, including the NA values are shown and any scores not observed, e.g., computational methods didn't have any 2 values observed and this figure now shows that as being "0"

```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (A) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users. (B) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used. (C) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used. (D) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g. a methods paper.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}

rrpp <- import_notes()
theme_set(theme_classic())
A <- ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
  geom_bar(fill = "black") +
  ylab("Score") +
  xlab(NULL) +
  ggtitle(label = "Computational methods availability")

B <- ggplot(rrpp, aes(y = software_avail)) +
  geom_bar(fill = "black") +
  xlab(NULL) +
  ylab(NULL) +
  ggtitle(label = "Software availability")

C <- ggplot(rrpp, aes(y = software_cite)) +
  geom_bar(fill = "black") +
  ylab("Score") +
  ggtitle(label = "Software citatations")

D <- ggplot(rrpp, aes(y = data_avail)) +
  geom_bar(fill = "black") +
  ylab(NULL) +
  ggtitle(label = "Data availability")

# put them all together
p <- (A | B) / (C | D)
p <- p + plot_annotation(tag_levels = "A",
                         title = "Aggregated article scores")
ggsave(filename = "../figures/Sparks et al Figure 2.eps",
       plot = p,
       width = 6,
       height = 6,
       units = "in",
       device = cairo_ps)
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 2.eps"),
   outfile = ("../figures/Sparks et al Figure 2.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
```

@@

    Question->Methodology->Data->Analysis
    Analysis->Manuscript
    Methodology->Description
    Methodology->Citation
    Methodology->Availability
    Manuscript->Supplement
    Data->'Data File'->'Public Repository'
    Data->Metadata->'Public Repository'
    Analysis->'Binary Code'->Supplement
    Analysis->'Source Code'->'Public Repository'
    Data->'Binary File'->Supplement
  }",
  width = 1000,
  height = 750
))
rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 3.eps")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 3.eps"),
   outfile = ("../figures/Sparks et al Figure 3.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 3.eps")
```

>>>>

```{r reproScore, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Reproducibility scores of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals. Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a "}
p <-
  ggplot(data = rrpp, aes(x = reproducibility_score)) +
  geom_histogram(binwidth = 10,
                 fill = "black") +
  ggtitle("Reproducibility index value")

ggsave(filename = "../figures/Sparks et al Figure 2.eps",
       plot = p,
       width = 6,
       height = 6,
       units = "in",
       device = cairo_ps)
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 2.eps"),
   outfile = ("../figures/Sparks et al Figure 2.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 2.eps")
```

```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (A) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users. (B) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used. (C) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used. (D) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g. a methods paper.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}
theme_set(theme_classic())

rrpp_long <-
  pivot_longer(rrpp,
               cols = c(
                 "comp_mthds_avail",
                 "software_avail",
                 "software_cite",
                 "data_avail"
               ))

p <- ggplot(rrpp_long, aes(x = as.factor(value))) +
  geom_bar(fill = "black") +
  ylab("Count") +
  xlab("Article Score") +
  ggtitle("Aggregated article scores") +
  facet_wrap(name ~ .)
p <- tag_facet(p = p, tag_pool = LETTERS, x = 5, family = "Arial")

ggsave(filename = "../figures/Sparks et al Figure 3.eps",
       plot = p,
       width = 6,
       height = 6,
       units = "in",
       device = cairo_ps)
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 3.eps"),
   outfile = ("../figures/Sparks et al Figure 3.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 3.eps")
```

@@

    Question->Methodology->Data->Analysis
    Analysis->Manuscript
    Methodology->Description
    Methodology->Citation
    Methodology->Availability
    Manuscript->Supplement
    Data->'Data File'->'Public Repository'
    Data->Metadata->'Public Repository'
    Analysis->'Binary Code'->Supplement
    Analysis->'Source Code'->'Public Repository'
    Data->'Binary File'->Supplement
  }",
  width = 1000,
  height = 750
))

rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 4.eps")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 4.eps"),
   outfile = ("../figures/Sparks et al Figure 4.eps"),
   options = "-dEPSCrop"
)

knitr::include_graphics(path = "../figures/Sparks et al Figure 4.eps")
```
